---
title: 'Data Viz: Homework 11'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##1. Setup
### options
Set up global options
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy=TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=70))
knitr::opts_chunk$set(fig.height=4, fig.width=6)
```

### libraries
Load in needed libraries 
```{r, include=FALSE}
library(tidyverse)
library(RColorBrewer)
library(ggplot2)
#library(haven)
#library(plotly)
#install.packages('rgl')
#library(rgl)
library(ISLR)
```

## 2. File management
### Create variables for directories
```{r file_management, include=FALSE}
project.dir <- getwd() #naeem
output.dir <- "/Output"
data.dir <- "C:/Users/Naeem Cho/Desktop/School Work/Data_Viz/Datasets"
setwd(project.dir)
getwd()
```

## 3. Importing Data
```{r, echo = FALSE, include=FALSE}
crab.df <- read_csv(file.path(data.dir, "crab.csv"))
```


## 1. Visualizing Interactions
Refer to the horseshoe crab dataset on Canvas. Using the existing color variable, create a new color variable with only *two categories*, medium (which consists of all colors that have "medium" in their name) and dark.

```{r}
crab <- crab.df %>% 
  mutate(sat = satellite > 0) %>% 
  mutate(color1 = fct_recode(factor(color), medium = "1", medium = "2", medium = "3", dark = "4"), weight  = weight/1000)


```


  a. Fit a logistic regression model that includes both **width** and **color** (the new variable) as predictors. Explain and visualize the effect of width. (You can refer to the *Solutions to HW10* handout to revisit what we discussed in class.)
  
```{r}
# Creating the logistic regression model
fit1 <- glm(sat ~ width + color1, family = binomial(link = logit), data = crab)
# Checking for statistical significance.
summary(fit1)
```

```{r}
# Computing the increase in odds
exp(0.4782)
exp(-1.3005)
```

```{r}
# Computing the confidence intervals
exp(confint(fit1))
```

__Interpretation__: The odds of  a satellite nearby are predicted to increase 1.6 fold (With a 95% confidence interval of 1.33 to 2.00) for every 1kg increase in the width of a crab.

  b. Explain the effect of color for this model. Is the effect of color the same at any given width?


  
  c. Fit the logistic regression model that allows an interaction between width and color. Visualize the fitted log-odds and the fitted probabilities. Explain the effect of width.
  
```{r}
# Logistic Regression with Interaction
fit2 <- glm(sat ~ width + color1 + width*color1,family = binomial(link = logit), crab)

# Summary with hypothesis testing results
summary(fit2)
```
  
  
```{r}
# forming the data
width.new <- seq(0, max(crab$width), 3)


mygrid <- expand.grid(width = width.new, color1 = crab$color1)
head(mygrid)
```

```{r}
predictions <- predict(fit2, newdata = mygrid, type = "link", se.fit = TRUE)

plotdata <- tibble(
  width = mygrid$width,
  color1 = mygrid$color1,
  log.odds = predictions$fit,
  log.odds.LB = log.odds - 1.96*predictions$se.fit,
  log.odds.UB = log.odds + 1.96*predictions$se.fit,
  prob = exp(log.odds)/(1+exp(log.odds)),
  prob.LB = exp(log.odds.LB)/(1+exp(log.odds.LB)),
  prob.UB = exp(log.odds.UB)/(1+exp(log.odds.UB))
)

mycol <- brewer.pal(8, "Dark2")[4:1]

plot.log.odds <- ggplot(data = plotdata, aes(x = width, y = log.odds, color = color1)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = log.odds.LB, ymax = log.odds.UB, fill = color1), color = NA, alpha = 0.5) +
  scale_color_manual(values = mycol, name = "Color:") +
  scale_fill_manual(values = mycol, name = "Color:") +
  theme_bw() +
  theme(legend.position = "top") +
  labs(title = "Log-Odds of Satellite Distance vs. Crab Width") +
  xlab("Width") +
  ylab("Log-Odds")
  
plot.log.odds


plot.probs <- ggplot(data = plotdata, aes(x = width, y = prob, color = color1)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = prob.LB, ymax = prob.UB, fill = color1), color = NA, alpha = 0.5) +
  scale_color_manual(values = mycol, name = "Color:") +
  scale_fill_manual(values = mycol, name = "Color:") +
  theme_bw() +
  theme(legend.position = "top") +
  labs(title = "Probability of Satellite distance vs. Width By Crab Color") +
  xlab("Width") +
  ylab("Probability")
  
plot.probs

```

  d. Perhaps a linear effect of width (on the log-odds scale) is too restrictive. Fit the model that allows a smooth effect of width by using splines, i.e, use `s(width)` instead of `width` in the right-hand side of the model formulation, and use `gam` from the `mgcv` R library instead of `glm` for fitting the model. Please refer to the two most recent R handouts on *Visualizing Uncertainty* and *Regression Splines in Poisson Models*. Kepp color in the model as a regular effect. Vizualize the fitted model both on the log-odds scale and the probability scale. How would you interpret the effect of width?
  